Flip score characterisation

### 2018-06-08 analysis/analyses/3-metric_characterisation/4-edge_flip.Rmd
rename dyntoy function

Generate different trajectory topologies
```{r}
topologies <- eval(formals(dyntoy:::generate_toy_milestone_network)$model)
topologies <- topologies[topologies != "BA"]
networks_synthetic <- map(topologies, dyntoy:::generate_toy_milestone_network) %>% tibble(milestone_network = ., topology = topologies)
```

>>>>

Generate different trajectory topologies
```{r}
topologies <- eval(formals(dyntoy:::generate_milestone_network)$model)
topologies <- topologies[topologies != "BA"]
networks_synthetic <- map(topologies, dyntoy:::generate_milestone_network) %>% tibble(milestone_network = ., topology = topologies)
```
